Supplementary Materials for ``Frustration shapes multi-channel Kondo physics: a star graph perspective"

### 2023-04-19 MCK-manuscript/MCK-manuscript.tex
finalised all changes to manuscript

{\color{blue}The work is split into seven major sections. In Sections 2 and 3, we describe the URG method mentioned above, apply it to obtain the renormalisation group (RG) flows of the multichannel Kondo model, and explore some properties of the zero bandwidth limit of the RG fixed point Hamiltonian. In Sections 4 and 5, we study the gapless excitations on top of the zero bandwidth limit. In Section 6, we discuss some duality transformation properties of the MCK model. In Section 7, we look into the effects of channel anisotropy. We finally conclude with some discussions of the results in Section 8.}

\subsection*{Summary of main results}
\begin{itemize}
	\item We elucidate, within the the context of the multichannel Kondo problem, the importance of the zero bandwidth limit of the RG fixed point Hamiltonian. We show that this zero bandwidth Hamiltonian directly leads to several properties of the MCK problem, like the ground-state magnetisation, scattering phase shift, Wilson loop and 't Hooft operators and degree of compensation.
	\item The ground-state degeneracy of the zero bandwidth Hamiltonian is found to be topological in nature: the orthogonal states can be explored by the application of twist operators. Integrating out the impurity from the conduction bath states leads to the emergence of a topologically degenerate local Mott liquid.
	\item We also demonstrate that the effective Hamiltonian for the gapless excitations of the fixed point Hamiltonian is of the non-Fermi liquid kind, involving scattering process that connect multiple conduction channels and leading to an orthogonality catastrophe in the ground-state. In momentum space, the self-energy resembles that of a marginal Fermi liquid localised near the impurity spin. 
	\item We link the non-Fermi liquid behaviour and orthogonality catastrophe with an ``unrenormalised" scattering phase shift; we show that this phase shift also leads to the well-known anomalous behaviour of quantities like the specific heat, magnetic susceptibility and thermal entropy.
	\item By combining the strong-weak duality of the MCK Hamiltonian with that of the RG equations, we show that the strong-coupling theory is constrained to be of a simple form. We also discuss an additional duality transformation that ``exchanges" the number of channels and impurity spin. This property allows us to infer the RG scaling behaviour of one of the models if we know that of the other.
\end{itemize}

>>>>

The work is split into seven major sections. In Sections 2 and 3, we describe the URG method mentioned above, apply it to obtain the renormalisation group (RG) flows of the multichannel Kondo model, and explore some properties of the zero bandwidth limit of the RG fixed point Hamiltonian. In Sections 4 and 5, we study the gapless excitations on top of the zero bandwidth limit. In Section 6, we discuss some duality transformation properties of the MCK model. In Section 7, we look into the effects of channel anisotropy. We finally conclude with some discussions of the results in Section 8.

\subsection*{Summary of main results}
\begin{itemize}
	\item We elucidate, within the the context of the multichannel Kondo problem, the importance of the zero bandwidth limit of the RG fixed point Hamiltonian. We show that this zero bandwidth Hamiltonian directly leads to several properties of the MCK problem, like the ground-state magnetisation, scattering phase shift, Wilson loop and 't Hooft operators and degree of compensation.
	\item The ground-state degeneracy of the zero bandwidth Hamiltonian is found to be topological in nature: the orthogonal states can be explored by the application of twist operators. Integrating out the impurity from the conduction bath states leads to the emergence of a topologically degenerate local Mott liquid.
	\item We also demonstrate that the effective Hamiltonian for the gapless excitations of the fixed point Hamiltonian is of the non-Fermi liquid kind, involving scattering process that connect multiple conduction channels and leading to an orthogonality catastrophe in the ground-state. In momentum space, the self-energy resembles that of a marginal Fermi liquid localised near the impurity spin. 
	\item We link the non-Fermi liquid behaviour and orthogonality catastrophe with an ``unrenormalised" scattering phase shift that can be obtained from the zero bandwidth problem; we show that this phase shift also leads to the well-known anomalous behaviour of quantities like the specific heat, magnetic susceptibility and thermal entropy.
	\item Various entanglement measures, e.g., impurity entanglement entropy and impurity-bath mutual information, for the overscreened case show discontinuous behaviour as the conduction bath states beyond the zero-bandwidth problem are re-introduced via single-electron hopping. These discontinuities do not exist in the single-channel problem, and arise from the orthogonality catastrophe present in the overscreened ground-state.
	\item By combining the strong-weak duality of the MCK Hamiltonian with that of the RG equations, we show that the strong-coupling theory is constrained to take a simple form. We also discuss an additional duality transformation connecting underscreened and overscreened models that involves exchanging the number of channels and impurity spin: this allows us to infer the infrared scaling behaviour of one  class of models from a knowledge of the other.
\end{itemize}

### 2023-04-19 MCK-manuscript/Supplementary/MCK-supplementary.tex
finalised all changes to manuscript

>>>>

\subsection{Stability of strong coupling fixed point in the overscreened and underscreened models}
We recall briefly the contrasting stability of the strong coupling fixed point in the overscreened and underscreened multichannel Kondo problems. As pointed out in Ref.\cite{Noz_blandin_1980}, adding electronic tunnelling from the conduction bath to the zero-bandwidth model reveals an effective Heisenberg exchange interaction between the effective spin ($\vec{S}^{*}$) of the zero-bandwidth model and the bath electrons (of the various channels $l=1,\ldots,K$) proximate to it: $H_{\mathrm{eff}} \sim J_{\mathrm{eff}}\sum_{l=1}^{K} \vec{S}^{*}\cdot\vec{S}^{(1)}_{l}$, where $J_{\mathrm{eff}}\sim \mathrm{sgn}(K-2S) t^{2}/J$ and $S^{*}=|K-2S|$. For the underscreened case $K<2S$, $J_{\mathrm{eff}}<0$ is ferromagnetic in nature; on the other hand, for the overscreened case $K>2S$, $J_{\mathrm{eff}}>0$ is antiferromagnetic. The opposite nature of the effective interaction arises from the fact that the Pauli exclusion principle favours electronic hopping from the conduction bath into the zero-bandwidth model for $\vec{S}^{*}$ being aligned (antialigned) with the incoming bath electrons for $K<2S$ ($K>2S$). Accordingly, $J_{\mathrm{eff}}$ is found to be RG irrelevant for the underscreened case, and leads to the strong coupling fixed point for the Kondo coupling $J$ being stable. On the other hand, $J_{\mathrm{eff}}$ is found to be RG relevant for the overscreened case and leads to a stable fixed point at intermediate coupling. Together with the duality relation between overscreened and underscreened multichannel Kondo problems discussed in Sec. 6 of the main manuscript, this allows us to infer the scaling behaviour of one class of models from a knowledge of the other.
